### 2020-04-22 README.Rmd
fixed errors docu and testhat

devtools::install_github("c1au6i0/rstract", auth_token = "355580fb57d57b58228b4617c14c3f8234741715")
```

@@

```{r all, message=FALSE}
all_us <- getus_all()

all_it <- getus_all()
```

## U.S. Datasets and sources

@@

## Datasets Italy

>>>>

devtools::install_github("c1au6i0/covid19census", auth_token = "355580fb57d57b58228b4617c14c3f8234741715")
```

@@

```{r all, message=FALSE}
library(covid19census)

# to retrive u.s data
all_us <- getus_all()

# to retrive italy data
all_it <- getit_all()
```

## U.S. Datasets and Sources

@@

## Italy: Datasets and Sources
